---
title: "Salaries_SoftwareDevelopers"
author: "André"
date: "2022-12-27"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

# Software Industry Salary Dataset - 2022
### This dataset contains information of salaries of various job profiles in India
The salary values are monthly and in USD

## Process data
Load required packages
```{r loading package}
require(tidyverse)

```

Import and prepare dataset <br/>
```{r import}
salaries_data_r <- read_csv("Salary_Dataset_with_Extra_Features.csv")
```

Changing column names to a more apropriate format
```{r correct column names}
colnames(salaries_data_r)[3] <- "job_title";
colnames(salaries_data_r)[2] <- "company_name"
colnames(salaries_data_r)[8] <- "job_roles"
colnames(salaries_data_r)[5] <-  "salaries_reported"

```


Converting the salary values from rupees to US Dollars
```{r convertion}
salaries_data<- salaries_data_r %>% 
  mutate(salary_d = Salary*0.12)
```

# Charts

## Salaries per jobs

### Top 10 best paying jobs
```{r tenBestJobs}
salaries_data %>%
  group_by(job_title) %>%
  summarize(average_salary = mean(salary_d)) %>%
  arrange(desc(average_salary)) %>% 
  slice(1:10) %>% 
  ggplot()+
  geom_col(mapping = aes(x = average_salary ,y=reorder(job_title, average_salary) ), fill="darkblue") +    
  scale_x_continuous(labels=scales::dollar_format()) +          ## Axis labels
  labs(title= "Top 10  best paying jobs")+ theme(plot.title = element_text(hjust = 0.5)) +    ##Titulo
  ylab("Job Title") + xlab("Average Salary")+ theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) + theme(axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))+    ##Axis
  geom_text(aes(x = average_salary, y = reorder(job_title, average_salary), label = format(floor(average_salary),digits=10)),position = position_dodge(width = 0.9),hjust = 1.1, color="white", fontface="bold")
```

### Top 10 worst paying jobs
```{r tenWorstJobs}
salaries_data %>%
  group_by(job_title) %>%
  summarize(average_salary = mean(salary_d)) %>%
  arrange(average_salary) %>%
  slice(1:10) %>% 
  ggplot()+
  geom_col(mapping = aes(x = average_salary ,y=reorder(job_title, average_salary) ), fill="darkblue") +    
  geom_col(mapping = aes(x = average_salary ,y=reorder(job_title, average_salary) ), fill="darkblue") +    
  scale_x_continuous(labels=scales::dollar_format()) +          ## Axis labels
  labs(title= "Top 10  worst paying jobs")+ theme(plot.title = element_text(hjust = 0.5)) +    ##Titulo
  ylab("Job Title") + xlab("Average Salary")+ theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) + theme(axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))+    ##Axis
  geom_text(aes(x = average_salary, y = reorder(job_title, average_salary), label = format(floor(average_salary),digits=10)),position = position_dodge(width = 0.9),hjust = 1.1, color="white", fontface="bold")
```

### Top 10 worst paying jobs excluding internships
```{r tenWorstJobsNI}
salaries_data %>%
  filter(!grepl("Intern", job_title)) %>%
  group_by(job_title) %>%
  summarize(average_salary = mean(salary_d)) %>%
  arrange(average_salary) %>%
  slice(1:10) %>% 
  ggplot()+
  geom_col(mapping = aes(x = average_salary ,y=reorder(job_title, average_salary) ), fill="darkblue") +    
  scale_x_continuous(labels=scales::dollar_format()) +          ## Axis labels
  labs(title= "Top 10  worst paying jobs", subtitle = "Excluding internships")+ theme(plot.title = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5)) +    ##Titulo
  ylab("Job Title") + xlab("Average Salary")+ theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) + theme(axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))+    ##Axis
  geom_text(aes(x = average_salary, y = reorder(job_title, average_salary), label = format(floor(average_salary),digits=10)),position = position_dodge(width = 0.9),hjust = 1.1, color="white", fontface="bold")
  
```

## Salary per company

### Top 10 best paying companies
```{r tenBestCompanies}
salaries_data %>% 
  group_by(company_name) %>% 
  summarize(average_salary=mean(salary_d)) %>% 
  arrange(desc(average_salary)) %>% 
  slice(1:10) %>% 
  ggplot()+
    geom_col(mapping=aes(x= average_salary, y=reorder(company_name, average_salary)),fill="darkblue")+
    scale_x_continuous(labels=scales::dollar_format()) +                                     ## Axis labels
    labs(title= "Top 10 best paying companies")+ theme(plot.title = element_text(hjust = 0.5))+      ## Title
    geom_text(aes(x= average_salary, y=reorder(company_name, average_salary), label = format(floor(average_salary),digits=10)),hjust=0.75, color="red", fontface="bold")+
    ylab("Company Name") + xlab("Average Salary")+ theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) + theme(axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

```

### Top 10 worst paying comapnies
```{r tenWorstCompanies}
salaries_data %>% 
  group_by(company_name) %>% 
  summarize(average_salary=mean(salary_d)) %>% 
  filter(company_name != "....") %>%
  arrange(average_salary)%>% 
  slice(1:10) %>% 
  ggplot()+
  geom_col(mapping=aes(x= average_salary, y=reorder(company_name, average_salary)),fill="darkblue")+
  scale_x_continuous(labels=scales::dollar_format()) +                                     ## Axis labels
  labs(title= "Top 10 worst paying companies")+ theme(plot.title = element_text(hjust = 0.5))+      ## Title
  geom_text(aes(x= average_salary, y=reorder(company_name, average_salary), label = format(floor(average_salary),digits=10)),hjust=1.2,        color="white", fontface="bold")+
  ylab("Company Name") + xlab("Average Salary")+ theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +  theme(axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

```

## Salary per location
```{r Salary location}
salaries_data %>% 
  group_by(Location) %>% 
  summarize(average_salary=mean(salary_d)) %>% 
  arrange(average_salary)%>% 
  ggplot()+
  geom_col(mapping=aes(x= average_salary, y=reorder(Location, average_salary)),fill="darkblue")+
  scale_x_continuous(labels=scales::dollar_format()) +                                     ## Axis labels
  labs(title= "Average salary per city")+ theme(plot.title = element_text(hjust = 0.5))+      ## Title
  geom_text(aes(x= average_salary, y=reorder(Location, average_salary), label = format(floor(average_salary),digits=10)),hjust=1.2, color="white", fontface="bold")+
  ylab("City") + xlab("Average Salary")+ theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) + theme(axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

```

## Pay by roles
```{r Salary roles}
salaries_data %>% 
  group_by(job_roles) %>% 
  summarize(average_salary=mean(salary_d)) %>% 
  arrange(average_salary)%>% 
  ggplot()+
  geom_col(mapping=aes(x= average_salary, y=reorder(job_roles, average_salary)),fill="darkblue")+
  scale_x_continuous(labels=scales::dollar_format()) +                                     ## Axis labels
  labs(title= "Average salary per roles")+ theme(plot.title = element_text(hjust = 0.5))+      ## Title
  geom_text(aes(x= average_salary, y=reorder(job_roles, average_salary), label = format(floor(average_salary),digits=10)),hjust=1.2, color="white", fontface="bold")+
  ylab("Role") + xlab("Average Salary")+ theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) + theme(axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

```

## Average salary reports
```{r calculate reports average}
salaries_data %>%
  summarize(average_reports = mean (salaries_reported))
```
A low average number of reports, *1.82* in this cases, indicates that the data may not be accurate and more data should be collected.

